### 2016-08-26 intro.tex
cheers

\section{Introduction}
\label{sec:intro}
\tsnote{Skeleton text from old intro.  (Full version of old intro now
  in an appendix.} \jnote{Too focused on Bloom filters for my
  taste.}
We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admitting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if
\[
(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),
\]
returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

>>>>

\section{Introduction}
\label{sec:intro}
\jnote{Too focused on Bloom filters for my taste.}
\tsnote{Yep, it's just a placeholder, with most of the NY-bashing cut out.  Doesn't reflect our updated/current level of generality.}
We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admitting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if
\[
(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),
\]
returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.
